NGO analysis

### 2022-07-31 Dashboard/report.Rmd
Removing errant \n in currency caption.

## Currency caption-----------------------------------------------------------
# Real currency caption
currency_caption <- ifelse(length(unique(html_currency$valutakode)) == 1,
      "", "Note: not all values are denominated in the same currency.\n"
    )
```

>>>>

## Currency caption-----------------------------------------------------------
currency_caption <- ifelse(length(unique(html_currency$valutakode)) == 1,
      "", "Note: not all values are denominated in the same currency."
    )
```
